---
title: "Happy Valentines Day"
author: "David M Vermillion"
date: "2/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Background

Happy Valentines Day my beloved Shayla!

As you know, I enjoy dabbling in all things visualization and math. I figured a delightful gift for you would be to create a little card telling how much I love you, utilizing some mathiness. I used one of my graphing programs (ggplot2) to generate the message shown below in two ways.



```{r image_grobs, fig.show = "hold", out.width = "30%", fig.align = "default"}

knitr::include_graphics("I.svg")

knitr::include_graphics("Heart2.svg")

knitr::include_graphics("U.svg")


```


________________________________________________________________________________


```{r fig.show = "hold", out.width = "50%", fig.align = "center"}

knitr::include_graphics("I.svg")

```

```{r fig.show = "hold", out.width = "25%", fig.align = "default"}

knitr::include_graphics("L.svg")

knitr::include_graphics("O.svg")

knitr::include_graphics("V.svg")

knitr::include_graphics("E.svg")

```

```{r fig.show = "hold", out.width = "50%", fig.align = "center"}


knitr::include_graphics("U.svg")
```

I also wanted to show you another heart I created to expressed my love.

```{r fig.show = "hold", out.width = "50%", fig.align = "default"}

knitr::include_graphics("Heart1.svg")

```

These are the equations I used to make the letters and the hearts, with the exception of the I and O, which I created using graph code.

$\LARGE y = \frac{1}{x}$
```{r fig.show = "hold", out.width = "50%", fig.align = "default"}

knitr::include_graphics("L.svg")

```


$\LARGE y=\lvert x\rvert$
```{r fig.show = "hold", out.width = "50%", fig.align = "default"}

knitr::include_graphics("V.svg")

```


$\LARGE x=-3\lvert sin(y)\rvert$
```{r fig.show = "hold", out.width = "50%", fig.align = "default"}

knitr::include_graphics("E.svg")

```



$$\begin{align} \LARGE x=4(3sin(\theta) - sin(3\theta))\\
\LARGE y=13cos(\theta) - 5cos(2\theta) - cos(4\theta) \end{align}$$
```{r fig.show = "hold", out.width = "50%", fig.align = "default"}

knitr::include_graphics("Heart1.svg")

```


$\LARGE r(\theta) = 2-2sin\theta+sin\theta \frac{\sqrt{\lvert cos\theta \rvert}}{sin\theta + 1.4}$
```{r fig.show = "hold", out.width = "50%", fig.align = "default"}

knitr::include_graphics("Heart2.svg")

```

With love from your adoring husband,

David