---
title: "Happy Valentines Day"
author: "David M Vermillion"
date: "2/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Background

Happy Valentines Day my beloved Shayla!

As you know, I enjoy dabbling in all things visualization and math. I figured a delightful gift for you would be to create a little card telling how much I love you, utilizing some mathiness. I used one of my graphing programs (ggplot2) to generate the graphs shown below.

First, I wanted to use math to say that I love you.

``` {r, echo=FALSE, message=FALSE, warning=FALSE}
# Letters
    library(tidyverse)
    t <- seq(-pi,pi,0.01)
    x <- 16*0.25*(3*sin(t) - sin(3*t))
    y <- 13*cos(t) - 5*cos(2*t) - cos(4*t)

    point1 <- 0
    point2 <- 0
    I <- tibble(point1, point2)

    IPlot <- I %>% 
      ggplot(aes(point1, point2)) +
      theme_classic() +
      geom_errorbar(ymin=-1, ymax=1, width=0.2, size=4, color="pink") +
      expand_limits(x=c(-.5,.5), y=c(-1.5,1.5)) +
      theme(axis.title.y = element_blank(),
            axis.title.x = element_blank(),
            plot.title = element_blank(),
            axis.line = element_blank(),
            axis.ticks = element_blank(),
            axis.text = element_blank())
    IPlot
```
I also wanted to show you a few hearts I created to expressed my love.

# Code

These are the equations I used to make the letters and the hearts

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```
