---
title: "Happy Valentines Day"
author: "David M Vermillion"
date: "2/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Background

Happy Valentines Day my beloved Shayla!

As you know, I enjoy dabbling in all things visualization and math. I figured a delightful gift for you would be to create a little card telling how much I love you, utilizing some mathiness. I used one of my graphing programs (ggplot2) to generate the graphs shown below.

First, I wanted to use math to say that I love you.

``` {r, echo=FALSE, message=FALSE, warning=FALSE}
# Letters
    library(tidyverse)
    t <- seq(-pi,pi,0.01)
    x <- 16*0.25*(3*sin(t) - sin(3*t))
    y <- 13*cos(t) - 5*cos(2*t) - cos(4*t)

# Plot I----

point1 <- 0
point2 <- 0
I <- tibble(point1, point2)

IPlot <- I %>% 
  ggplot(aes(point1, point2)) +
  theme_classic() +
  geom_errorbar(ymin=-1, ymax=1, width=0.2, size=4, color="pink") +
  expand_limits(x=c(-.5,.5), y=c(-1.5,1.5)) +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        plot.title = element_blank(),
        axis.line = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank())
IPlot


# Plot L ------------------------------------------------------------------

x2 <- seq(1,100,.1)
y2 <- 1/x2
L <- tibble(x2,y2)

LPlot <- L %>% 
  ggplot(aes(x2,y2)) +
  theme_classic() +
  geom_line(size = 4, color = "pink", lineend = "round") +
  expand_limits(x=c(-90,200), y=c(0,1.1)) +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        plot.title = element_blank(),
        axis.line = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank())
LPlot


# Plot O ------------------------------------------------------------------

CirclePlot <- I %>% 
  ggplot(aes(point1, point2)) +
  theme_classic() +
  geom_point(size = 150, color = "pink") +
  geom_point(size = 142, color = "white") +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        plot.title = element_blank(),
        axis.line = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank())
CirclePlot


# Plot V ------------------------------------------------------------------

x4 <- seq(-3, 3, 0.1)
y4 <- abs(x4)
V <- tibble(x4,y4)

VPlot <- V %>% 
  ggplot(aes(x4, y4)) + 
  theme_classic() +
  geom_line(size = 4, color = "pink", lineend = "round") +
  expand_limits(x=c(-4.5, 4.5), y=c(0, 3)) +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        plot.title = element_blank(),
        axis.line = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank())
VPlot


# Plot E ------------------------------------------------------------------

y6 <- seq(-pi, pi, 0.001)
x6 <- -3*abs(sin(y6))
E <- tibble(x6, y6)

EPlot <- E %>% 
  ggplot(aes(x6, y6)) + 
  theme_classic() +
  expand_limits(x=c(-5, 3), y=c(-pi, pi)) +
  geom_point(color = "pink", size = 4) +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        plot.title = element_blank(),
        axis.line = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank())
EPlot


# Plot U ------------------------------------------------------------------

x5 <- seq(-3.1, 3, 0.1)
y5 <- (4*x5^4) + x5^3 + x5^2
U <- tibble(x5, y5)

UPlot <- U %>% 
  ggplot(aes(x5, y5)) +
  theme_classic() +
  geom_line(size = 4, color = "pink") +
  expand_limits(x=c(-5, 5), y=c(0, 400)) +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        plot.title = element_blank(),
        axis.line = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank())
UPlot
    
    
```


I also wanted to show you a few hearts I created to expressed my love.

``` {r, echo=FALSE, message=FALSE, warning=FALSE}
Heart1 <- tibble(x,y)

Heart1Plot <- Heart1 %>% 
  ggplot(aes(x,y)) +
  theme_classic() +
  geom_polygon(fill = "pink") +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        plot.title = element_blank(),
        axis.line = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank()) +
  
  coord_polar(start = pi)
Heart1Plot


r <- 2 - 2*sin(t) + sin(t)*(sqrt(abs(cos(t))))/(sin(t)+1.4)

Heart2 <- tibble(t,r)

Heart2Plot <- Heart2 %>% 
  ggplot(aes(t,r)) +
  theme_classic() +
  geom_polygon(fill = "pink") +
  coord_polar(start = pi/2) +
  scale_fill_manual(values = "pink") +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        plot.title = element_blank(),
        axis.line = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank())
Heart2Plot
```

This of course also leads to one last way to express my love:

```  {r, echo=FALSE, message=FALSE, warning=FALSE}
IPlot
Heart2Plot
UPlot

```

```  {r, echo=FALSE, message=FALSE, warning=FALSE}
library(cowplot)
plot_grid(IPlot, Heart2Plot, UPlot, align = 'h', ncol = 1)

```

With love from your amazed husband,

David


# Code

These are the equations I used to make the letters and the hearts

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```
