---
title: "Your Nerdy Valentine's Day Card"
author: "David M Vermillion"
date: "2/14/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library('here')
here::i_am('Code/ValentinesDayCard.Rmd')
```


### Happy Valentine's Day my beloved Shayla!

### As you know, I enjoy dabbling in all things visualization and math. I figured a delightful gift for you would be to create a little card telling how much I love you, utilizing some mathiness. I used one of my graphing programs (ggplot2) to generate the message shown below in two ways.



```{r image_grobs, fig.show = "hold", out.width = "30%", fig.align = "default"}

knitr::include_graphics(here("Images/I.svg"))

knitr::include_graphics(here("Images/Heart2.svg"))

knitr::include_graphics(here("Images/U.svg"))


```


________________________________________________________________________________


```{r fig.show = "hold", out.width = "50%", fig.align = "center"}

knitr::include_graphics(here("Images/I.svg"))

```

```{r fig.show = "hold", out.width = "25%", fig.align = "default"}

knitr::include_graphics(here("Images/L.svg"))

knitr::include_graphics(here("Images/O.svg"))

knitr::include_graphics(here("Images/V.svg"))

knitr::include_graphics(here("Images/E.svg"))

```

```{r fig.show = "hold", out.width = "50%", fig.align = "center"}


knitr::include_graphics(here("Images/U.svg"))
```

### I also wanted to show you another heart I created to express my love.

```{r fig.show = "hold", out.width = "50%", fig.align = "center"}

knitr::include_graphics(here("Images/Heart1.svg"))

```

### These are the equations I used to make the letters and the hearts, with the exception of the I and O, which I created using graph code.

$\LARGE y = \frac{1}{x} \hspace{8cm}$
```{r fig.show = "hold", out.width = "50%", fig.align = "default"}

knitr::include_graphics(here("Images/L.svg"))

```


$\LARGE y=\lvert x\rvert \hspace{8cm}$
```{r fig.show = "hold", out.width = "50%", fig.align = "default"}

knitr::include_graphics(here("Images/V.svg"))

```


$\LARGE x=-3\lvert sin(y)\rvert \hspace{6cm}$
```{r fig.show = "hold", out.width = "50%", fig.align = "default"}

knitr::include_graphics(here("Images/E.svg"))

```


$\begin{align} & \LARGE x=4(3sin(\theta) - sin(3\theta))\\
&\LARGE y=13cos(\theta) - 5cos(2\theta) - cos(4\theta) \end{align}$
```{r fig.show = "hold", out.width = "50%", fig.align = "default"}

knitr::include_graphics(here("Images/Heart1.svg"))

```


$\LARGE r(\theta) = 2-2sin\theta+sin\theta \frac{\sqrt{\lvert cos\theta \rvert}}{sin\theta + 1.4} \hspace{1.2cm}$
```{r fig.show = "hold", out.width = "50%", fig.align = "default"}

knitr::include_graphics(here("Images/Heart2.svg"))

```

### With love from your adoring husband,

# David